Geometric variational problems

### 2020-11-15 NSF2020/Description/broaderimpacts.tex
RJR educational impact

\section{Broader Impacts of the Proposed Work}
\label{sec:BroaderImpacts}

@@

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The proposed research will have an immediate impact on undergraduate and
graduate education. At the undergraduate level, the project will include
and support undergraduate researchers from Fordham University. The
supported summer researchers will gain valuable first-hand
interdisciplinary experience in mathematical modeling and computation.
We will incorporate research into teaching, especially in differential
equation and programming courses. PI YNY will work on simple modeling of
self-assembly problems with both undergraduate and high school students
from Newark Science Park High School. PI YNY has a track record of
working with local high school students for their research projects
before they apply for colleges. PI BQ will work with undergraduate and
high school students through the Undergraduate Research Opportunity
Program and Young Scholar's Program as he has done in the past.

Over the past eight years, PI RR has included many undergraduates in the
execution of research initiatives and coauthoring publications. He has a
track record for supporting underrepresented groups, being called on by
the Collegiate Science and Technology Entry Program (CSTEP) to make
opportunities for promising students, for example. He has mentored two
Clare Boothe Luce Scholars, one a U.S.~Marine Corp veteran, and a high
school student in the NYU GSTEM program.

The PIs will capitalize on the synergy between both FSU's doctoral
program in Scientific Computing, NJIT's doctoral program in Mathematical
Sciences, and Fordham's undergraduate focus in the Department of
Mathematics. Promising, young undergraduate scientists from the Bronx
community will find a natural pipeline into graduate studies by working
directly or indirectly on this project. At the graduate-level, PI YNY
expects to train and support a PhD student for two more years. PI BQ
will advise a postdoctoral fellow for two years. The PIs will foster
vertical integration between the senior personnel, their collaborators,
postdocs, doctoral, and Bachelor students, enhancing the learning
environment.

>>>>

\section{Broader Impacts}
\label{sec:BroaderImpacts}

@@

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The topics of this proposal have application in robotics, machine learning,
and engineering. To foster training in mathematical sciences, the project
will include undergraduate researchers (URs). The proposal supports one UR
per year from the lead institution, and will include one or two additional
UR from actively supported in-house programs

The URs will work as a team for eight weeks in the summer. They will
collaborate directly with the senior personnel, have tutorials in topics
such as numerical quadrature and integral equations, and train in
mathematical writing and presentation. To maximize vertical integration,
and to the extent possible, the PIs and personnel will travel to 
New York for one or two weeks in the summers. Fordham University 
recently constructed a seminar/collaboration space specifically
for collaborative research, and URs will base there activitied from here.

As a requirement, the URs will write quality summary reports and give
presentations at the their respective research symposia. The work will be
considered a success if the URs also participate in a national conference.
The best possible outcome is if URs coauthor a publication.

There are two ways the proposal will meaningfully engage the community.
To be more impactful, students from the Bronx High School of Science
(PI RR) and Newark Science Park High School (PI YNY) will be encouraged
to join the research team. PI BQ will work with undergraduate and high
school students through the Undergraduate Research Opportunity Program
and Young Scholar's Program, as he has done in the past. Secondly, the
PIs will prioritize students who would most benefit from the grant activity.
We specifically target students whose socio-economic background prevents
them from participating in out-of-state research experiences.

Innovations in teaching: we will create several modules to include
in our courses. These modules will introduce topics from numerical linear
algebra and optimization, and be based on the ideas of the proposal.
Additionally, we and our UR collaborators will give remote, guest lectures
in each others' courses and undergraduate seminars.

%The proposed research will have an immediate impact on undergraduate and
%graduate education. At the undergraduate level, the project will include
%and support undergraduate researchers from Fordham University. The
%supported summer researchers will gain valuable first-hand
%interdisciplinary experience in mathematical modeling and computation.
%We will incorporate research into teaching, especially in differential
%equation and programming courses. PI YNY will work on simple modeling of
%self-assembly problems with both undergraduate and high school students
%from Newark Science Park High School. PI YNY has a track record of
%working with local high school students for their research projects
%before they apply for colleges. PI BQ will work with undergraduate and
%high school students through the Undergraduate Research Opportunity
%Program and Young Scholar's Program as he has done in the past.

%Over the past eight years, PI RR has included many undergraduates in the
%execution of research initiatives and coauthoring publications. He has a
%track record for supporting underrepresented groups, being called on by
%the Collegiate Science and Technology Entry Program (CSTEP) to make
%opportunities for promising students, for example. He has mentored two
%Clare Boothe Luce Scholars, one a U.S.~Marine Corp veteran, and a high
%school student in the NYU GSTEM program.

%The PIs will capitalize on the synergy between both FSU's doctoral
%program in Scientific Computing, NJIT's doctoral program in Mathematical
%Sciences, and Fordham's undergraduate focus in the Department of
%Mathematics. Promising, young undergraduate scientists from the Bronx
%community will find a natural pipeline into graduate studies by working
%directly or indirectly on this project. At the graduate-level, PI YNY
%expects to train and support a PhD student for two more years. PI BQ
%will advise a postdoctoral fellow for two years. The PIs will foster
%vertical integration between the senior personnel, their collaborators,
%postdocs, doctoral, and Bachelor students, enhancing the learning
%environment.
